API design for machine learning software: experiences from the scikit-learn project

### 2013-06-27 paper.tex
copyedit/trim: get scaler example back on its page

clf = LogisticRegression(penalty="l1")
clf.fit(X_train, y_train)
\end{pythoncode}
In this snippet, a \texttt{LogisticRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{"l1"}, hence enabling
$\ell_1$ regularization. Other hyper-parameters (such as \texttt{C}, which
defines the strength of the regularization) are not explicitly defined and are
thus set to the default values. Upon calling \texttt{fit}, the model is then
learned from the training arrays \texttt{X\_train} and \texttt{y\_train},
and stored within the object for later use.
%% (In this example, \texttt{fit} is called solely for its side effects.)
Since all estimators share the same interface, using a different learning algorithm is
as simple as replacing the constructor (the class name).
For example, to build a random forest on
the same training data, one would simply have to replace
\texttt{LogisticRegression(penalty="l1")} in the snippet above by
\texttt{RandomForestClassifier()}.

@@

Finally, predictors should also provide a \texttt{score} function to assess the
performance on some input data. In supervised learning estimators, this method
takes as input arrays \texttt{X\_test} and \texttt{y\_test} and typically
computes the coefficient of determination between \texttt{y\_test} and
\texttt{predict(X\_test)} in regression, or the accuracy
in classification. From an API point of view,
the only guideline is that the \texttt{score} method returns a value
that quantifies the quality of its predictions (the higher, the better).
Unsupervised learning estimators may also exposes a \texttt{score} function
to compute, for instance, the likelihood of the given data under its model.

>>>>

clf = LogisticRegression(penalty="l1")
clf.fit(X_train, y_train)
\end{pythoncode}
In this snippet, a \texttt{LogisticRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{"l1"} for
$\ell_1$ regularization. Other hyper-parameters (such as \texttt{C},
the strength of the regularization) are not explicitly given and
thus set to the default values. Upon calling \texttt{fit}, a model is
learned from the training arrays \texttt{X\_train} and \texttt{y\_train},
and stored within the object for later use.
%% (In this example, \texttt{fit} is called solely for its side effects.)
Since all estimators share the same interface, using a different learning algorithm is
as simple as replacing the constructor (the class name);
to build a random forest on
the same data, one would simply replace
\texttt{LogisticRegression(penalty="l1")} in the snippet above by
\texttt{RandomForestClassifier()}.

@@

Finally, predictors should also provide a \texttt{score} function to assess the
performance on some input data. In supervised learning estimators, this method
takes as input arrays \texttt{X\_test} and \texttt{y\_test} and typically
computes the coefficient of determination between \texttt{y\_test} and
\texttt{predict(X\_test)} in regression, or the accuracy
in classification.
The only requirement is that the \texttt{score} method return a value
that quantifies the quality of its predictions (the higher, the better).
Unsupervised learning estimators may also exposes a \texttt{score} function
to compute, for instance, the likelihood of the given data under its model.
